submission

### 2024-03-09 submission.Rmd
chore: merge

```{r,warning=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(MASS)
library(mixtools)
library(pwr)
library(mclust)
```

@@

The conclusion is that th Wilcoxon test breaks down with so few samples. The Wolcoxon table, which is used to obtain the $\alpha$, does not go below a sample size of 5. And in the case that all the values of one distribution is larger, it gives at most an $\alpha$ of 0.1. \
The other case would be to try and fit the data to a distribution. But with so few datapoints, that would be futile. \
The answer to the question is therefore no, one can not make any conclusions.

>>>>

```{r,warning=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(MASS)
library(mixtools)
library(pwr)
```

@@

The conclusion is that th Wilcoxon test breaks down with so few samples. The Wolcoxon table, which is used to obtain the $\alpha$, does not go below a sample size of 5. And in the case that all the values of one distribution is larger, it gives at most an $\alpha$ of 0.1.\
The other case would be to try and fit the data to a distribution. But with so few datapoints, that would be futile.\
The answer to the question is therefore no, one can not make any conclusions.
